An Improved ANS Transaction Template

### 2018-01-26 paper.tex
adding a snetce about storage
adding assay no recycling figs, cleanig bottom of the file

All cases will be considered with and without tail recycling. Figure
\ref{fig:flow} shows the different flows between the different facilities in the
fleet, in a configuration with two different levels of cascade without tail
recycling. When considering the tail recycling, all the flow going from a
cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occuring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{} and \ref{}, the first case is able to produce a an uranium product enrich
at $98\%$ while the second case is only able to reach an enrichment of $88.3\%$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection Goes Here}
\begin{equation} \label{eq:marshak}
  4 J^- = \phi + 2 D \vec{n} \vd \grad \phi \,.
\end{equation}
If we so choose, we can effortlessly reference the equation later.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics{example_figure}
  \caption{Captions are flush with the left.}
  \label{fig:voltage}
\end{figure}

Later on, we can include a table, even one that spans two columns such as
Table~\ref{tab:widetable}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Notice how the table reference uses a Roman numeral
for its numbering scheme, whereas the figure reference uses an Arabic numeral.
For one-column tables, use the \verb|table| environment; two-column tables use
\verb|table*|. The same applies to figures.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Another Subsection}
Excessive sectioning in a three-page document is discouraged, but here are more
subsections to demonstrate compliance with the ANS formatting guidelines.

\subsubsection{Third-level Heading}
This subsubsection shows compliance with the ANS-specified standard. This level
of heading should be used rarely.

\subsubsection{Another Such Heading}
And, if you really think you need a third-level heading, you should make sure
that your subsection needs at least two of them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

>>>>

All cases will be considered with and without tail recycling. Figure
\ref{fig:flow} shows the different flows between the different facilities in the
fleet, in a configuration with two different levels of cascade without tail
recycling. When considering the tail recycling, all the flow going from a
cascade to the waste, are going from the cascade $i$ to the cascade $i-1$. 
The Storage are not required in Cyclus they have been added to ensure the
proper material flow between the facilities (if a receiver facility input buffer
is full then the sender facility will stop sending material to it, and will stop
working when its own output buffer will be filled).

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling.}\label{fig:assay_c1_nc}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling.}\label{fig:assay_c2_nc}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
